Fast Neural Machine Translation Implementation

### 2018-05-17 wnmt.2018/wnmt.tex
turn on timings

\author{Hieu Hoang \\
  University of Edinburgh, Scotland \\
  {\tt hieu@hoang.co.uk} \\
  \And
  Tomasz Dwojak \\
  Adam Mickiewicz University \\
  {\tt t.dwojak@amu.edu.pl} \\
  \And
  Rihards Krislauks \\
  Tilde \\
  {\tt rihards.krislauks@tilde.lv} \\
  \And
  Daniel Torregrosa \\
  Universitat d’Alacant \\
  {\tt dtorregrosa@dlsi.ua.es} \\
  \And
  Kenneth Heafield \\
  University of Edinburgh, Scotland \\
  {\tt kheafiel@inf.ed.ac.uk} \\
  }

>>>>

  \author{Hieu Hoang$^{\dagger}$ \, Tomasz Dwojak$^{*}$ \, Rihards Krislauks$^{\ddagger}$ \\ {\bf Daniel Torregrosa$^{\mathparagraph}$ \, Kenneth Heafield$^{\dagger}$ } \\[2mm]
  $^{\dagger}$University of Edinburgh \, $^{*}$Adam Mickiewicz University in Pozna\'{n} \\ $^{\ddagger}$Tilde \,  $^{\mathparagraph}$Universitat d’Alacant }
